---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# jamesdemodata

<!-- badges: start -->
[![R-CMD-check](https://github.com/growthcharts/jamesdemodata/workflows/R-CMD-check/badge.svg)](https://github.com/growthcharts/jamesdemodata/actions)
[![R-CMD-check](https://github.com/growthcharts/jamesdemodata/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/growthcharts/jamesdemodata/actions/workflows/R-CMD-check.yaml)
<!-- badges: end -->

The `jamesdemodata` is a lightweight repo with demo and test children. The goal 
of the package is to test the 
**Joint Automatic Measurement and Evaluation System (JAMES)**.
JAMES is an **experimental** online resource for creating and analysing
growth charts.

## Installation

The following statements will install the `jamesdemodata` package

```{r eval = FALSE}
install.packages("remotes")
remotes::install_github("growthcharts/jamesdemodata")
```

## Example

Test en demo data are stored in the `inst/extdata` directory. In order to generate a file name of the SMOCC child Laura S use 

```{r}
fn <- system.file("extdata", "bds_v3.0", "smocc", "Laura_S.json", package = "jamesdemodata")
```

Read the data into R using the `bdsreader` package:

```{r}
library(bdsreader)
tgt <- read_bds(fn)
persondata(tgt)
timedata(tgt)
```

See <https://github.com/growthcharts/bdsreader> for installation notes of `bdsreader`.

