---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, eval=FALSE)
```

# jamestest

The `jamestest` is a simple Shiny app with demo children. The goal 
of the package is to test the website construction facility of the
**Joint Automatic Measurement and Evaluation System (JAMES)**.
JAMES is an **experimental** online resource for creating and analysing
growth charts.

## Installation

The following statements will install the `jamestest` package

```{r eval = FALSE}
install.packages("remotes")
remotes::install_github("stefvanbuuren/jamestest")
```

## Example

View the website locally, as follows:

```{r}
library(jamestest)
go()
```

The site will not run in the internal RStudio viewer. Click on 
button `Open in browser`. 

## Online version

You can spare yourself the trouble of installing the package, and visit 
`JAMES tryout` at <https://tnochildhealthstatistics.shinyapps.io/james_tryout/>.

## Resources

- [JAMES](https://github.com/stefvanbuuren/james)
