---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# jamesdemodata

<!-- badges: start -->
[![R-CMD-check](https://github.com/growthcharts/jamesdemodata/workflows/R-CMD-check/badge.svg)](https://github.com/growthcharts/jamesdemodata/actions)
[![R-CMD-check](https://github.com/growthcharts/jamesdemodata/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/growthcharts/jamesdemodata/actions/workflows/R-CMD-check.yaml)
<!-- badges: end -->

The `jamesdemodata` package is a lightweight repository containing demonstration data and example child records. Its goal is to provide reproducible examples and test cases for the **Joint Automatic Measurement and Evaluation System (JAMES)** — an online service that supports real-time decision making in the monitoring and prediction of child growth and development.

## 1. Installation

To install the `jamesdemodata` package from GitHub, use:

```{r eval = FALSE}
install.packages("remotes")
remotes::install_github("growthcharts/jamesdemodata")
```

## 2. A JSON schema for data exchange

The example datasets build upon the the [BDS JGZ specification](https://www.ncj.nl/onderwerp/digitaal-dossier-jgz/bds-jgz-versiebeheer/) and [NICTIZ informatiestandaarden JGZ](https://nictiz.nl/releases/jeugdgezondheidszorg-7-1-1/) These specifications provide a detailed description on what information can be collected and how it should stored. The `bdsreader` package implements a subset of BDS JGZ fields related to child growth and development into a JSON schema that can be used for validation and electronic data communication. The current version of this JSON schema is [`bds_v3.0`](https://raw.githubusercontent.com/growthcharts/bdsreader/refs/heads/master/inst/schemas/bds_v3.0.json). 

The examples in the `jamesdemodata` package are coded according to this JSON schema, or a previous version of it.

## 3. Usage `json/examples`

The `json/examples` directory contains a few minimal JSON datasets for testing and development.

### 3.1 Read the first 10 lines of a demo file

Use the `system.file()` function to construct the path to a file within the package:

```{r}
fn <- system.file("json", "examples", "maria.json", package = "jamesdemodata")
cat(paste(readLines(fn, n = 10), collapse = "\n"), "\n...")
```

### 3.2 Read JSON data into R using `bdsreader`

If you have the `bdsreader` package installed, you can read and inspect the JSON data as follows:

```{r}
library(bdsreader)
read_bds(fn)
```

For installation instructions and further documentation, see the [`bdsreader` GitHub repository](https://github.com/growthcharts/bdsreader).

### 3.3 Files in `json/examples` directory

To explore what is available in `json/examples` use

```{r}
json_path <- system.file("json", "examples", package = "jamesdemodata")
list.files(json_path, recursive = TRUE)
```

The following table lists the files in the `json/examples` directory, along with a brief description of each file.

```{r, results='asis', echo=FALSE}
descriptions <- c(
  "client3.json" = "Example child record in minimal JSON format",
   "Kevin_S.json" = "Preterm child Kevin_S using current JSON schema",
   "Laura_S.json" = "Example child Laura_S using current JSON schema",
   "maria.json" = "Example child record in minimal JSON format",
   "maria-mangled.json" = "Same child with vastly incomplete data, for debugging",
   "maria1.json" = "Example child record, JSON schema 1.0 (outdated)",
   "maria2.json" = "Example child record, JSON schema 2.0 (outdated)",
   "test.json" = "Example child record in minimal JSON format")

files <- list.files(json_path, recursive = TRUE)
cat("| File | Description |\n|------|-------------|\n")
for (f in files) {
  desc <- descriptions[f]
  if (is.null(desc)) desc <- ""
  cat(sprintf("| `%s` | %s |\n", f, desc))
}
```


## 4. Usage `extdata`

The `extdata` directory includes more comprehensive child records coded according to various versions of the BDS specification. These files are used by the [JAMES demo app](https://tnochildhealthstatistics.shinyapps.io/james_tryout/). 

For example, to see the first 10 lines of the `Laura_S.json` file, use:

```{r}
fn <- system.file("extdata", "bds_v3.0", "smocc", "Laura_S.json", package = "jamesdemodata")
cat(paste(readLines(fn, n = 10), collapse = "\n"), "\n...")
```

### 4.1 Subdirectories in `extdata`

The interesting parts of `extdata` are the example files using `bds_v3.0` schema:

```{r}
extdata <- system.file("extdata", package = "jamesdemodata")
dirs <- list.dirs(extdata, full.names = FALSE, recursive = TRUE)
dirs[grepl("^bds_v3\\.0", dirs)]
```


### 4.2 Exploring and working with `extdata` files

Each subdirectory contains 10 children. For example, let us explore the files in `bds_v3.0/smocc`:

```{r}
smocc <- system.file("extdata", "bds_v3.0", "smocc", package = "jamesdemodata")
list.files(smocc, recursive = TRUE)
```

See the first few lines of the `Anne_S.json` file:

```{r}
fn <- file.path(smocc, "Anne_S.json")
cat(paste(readLines(fn, n = 10), collapse = "\n"), "\n...")
```

As before, we can read read and inspect the JSON data using the `bdsreader` package:

```{r}
read_bds(fn)
```

